---
title: "p8105_hw1_JL5295"
author: "Jana Lee"
date: "9/17/2019"
output: github_document
---
# **Problem 1**
## Making the First Data Frame
```{r, first_df}
set.seed(10)

library (tidyverse)

problem1_df =tibble(
  sample=rnorm(8),
  logical_vector = sample > 0,
  char_vector = c("Help", "am", "I", "doing", "this", "correctly", "ahh", "ahh"),
  factor_vector = factor(c("red", "yellow", "blue", "red", "yellow", "blue","red", "red"))
)

mean(pull(problem1_df, sample))

mean(pull(problem1_df, logical_vector))

mean(pull(problem1_df, char_vector))

mean(pull(problem1_df, factor_vector))

```
**Problem 1 Comment** Problem 1 asks us to take a deep dive into creating a dataframe. problem1_df was created and allows us to explore different types of vectors. I set the seed here, so I can ensure reproducibility on this homework.

Then, I took the mean. The mean of sample is -0.2224873. Mean of logical_vector is 0.5. Both the mean of char_vector and factor_vector generated a warning message. This does explain what is happening when I try to take the mean because char_vector and factor_vector are not logical or numerical vectors.


## Second code chunk, with as.numeric function
```{r, as_numeric function, eval=FALSE}
# Convert the logical vector to numeric and multiply the random sample by 
# the result.
as.numeric (pull(problem1_df, logical_vector))*(pull(problem1_df, sample))

# Convert the logical vector to a factor and multiply the random sample by 
# the result.
as.factor (pull(problem1_df, logical_vector))*(pull(problem1_df, sample))

# Convert the logical vector to factor and then convert the result to nnumeric 
# and then multiply the random sample by the result.
as.numeric (as.factor (pull(problem1_df, logical_vector)))*(pull(problem1_df, sample))

```

# **Problem 2**
## Making a Second Data Frame
```{r, second_df}
set.seed(10)

problem2_df = tibble(
  x = rnorm (500),
  y = rnorm (500),
  logical_vector = x + y > 1,
  numeric_vector = as.numeric (logical_vector),
  factor_vector = as.factor (logical_vector),
)
```

The dataset has `r nrow(problem2_df)` rows and `r ncol(problem2_df)` columns.
The mean of x is `r mean(pull(problem2_df, x))`.
The median of x is `r median(pull(problem2_df, x))`.
The standard deviation of x is `r sd(pull(problem2_df, x))`.
The proportion of cases for which x + y > 1 is `r mean(pull(problem2_df, logical_vector))`.

## Scatterplots
```{r, scatterplots}
plota = ggplot(problem2_df, aes(x, y, color = logical_vector)) + geom_point()
plota

plotb = ggplot(problem2_df, aes(x, y, color = numeric_vector)) + geom_point()
plotb

plotc= ggplot(problem2_df, aes(x, y, color = factor_vector)) + geom_point()
plotc

ggsave("plota.png",)

```
**Scatterplot comment:** There are two colors for the logical_vector scatterplot, one red and one green. There is a gradient of sky blue to dark blue for the numeric_vector scatterplot. There are two colors for the factor_vector, one red and one green. Saved plota as a PNG file, and onfirmed it is in the File Directory.
