---
title: "Homework 1 JL5295"
author: "Jana Lee"
date: "9/17/2019"
output: html_document
---

Problem 1
```{r, creating_a_dataframe}
library (tidyverse)
problem1_df = tibble(
  sample=rnorm(8),
  logical_vector = sample > 0,
  char_vector = c("Help", "am", "I", "doing", "this", "correctly", "ahh", "ahh"),
  factor_vector = c("red", "yellow", "blue", "red", "yellow", "blue","red", "red")
)
```

# Finding the mean for each variable. 
For sample variable:
```{r}
mean_sample = mean(pull(problem1_df, sample))
```
Mean of sample is -0.2224873.

For logical_vector:
```{r}
mean_logical_vector = mean(pull(problem1_df, logical_vector))
```
Mean of logical_vector is 0.5.

For char_vector:
```{r}
mean_char_vector = mean(pull(problem1_df, char_vector))
```
Mean of char_vector generated a warning message that says: In mean.default(pull(problem1_df, char_vector)) :
 argument is not numeric or logical: returning NA.
 
For factor_vector:
```{r}
mean_factor_vector = mean(pull(problem1_df, factor_vector))
```
Mean of factor_vector generated a warning message that says: In mean.default(pull(problem1_df, char_vector)) :
 argument is not numeric or logical: returning NA.
 
 









